Eliminating Systematic Bias in Bright-Siren Multimessenger Observations of Compact Object Mergers from Inclination-Dependent Emission

### 2022-10-01 src/tex/ms.tex
Adding ack'n for KICP workshop.
Fix some typos, lower y-axis limits.

@@

Different EM counterparts will exhibit different dependence on inclination
angle.  In this subsection, we model an GW+EM catalog composed of two
components.  One component has EM detectable emission only very close to on/off
axis, with $P_{\detected,\EM} = 0$ unless $|x| \geq x_\mathrm{min}$ with
$x_\mathrm{min} = \cos 15^\circ$.  The other component has a (weak) preference
for on/off axis emission, with detectability varying quadratically from a
maximum at $|x| = 1$ to and 50\% of its maximum value at $x = 0$.  The two
components are mixed equally in the data set, so that the overall EM detection
efficiency is 
\begin{equation}
    P_{\detected,\EM}(x) \propto \frac{1}{2} \left( \frac{H\left( |x| - x_\mathrm{min} \right)}{x_\mathrm{min}} + \frac{3 \left( x^2 + 1/2 \right)}{5} \right),
\end{equation}
with $H$ the Heaviside step function.  We choose $N_l = 4$.  The logarithm of
this function is not expressible as any finite sum of Legendre polynomials, so
our model is incapable of exactly reproducing the shape of this detection
efficiency.  Nonetheless, we will see that we can still obtain sub-percent
accurate, un-biased estimates of $H_0$.

@@

\begin{acknowledgments}
    \todo{We thank people for stuff.}
\end{acknowledgments}

>>>>

\author{Friends}

@@

Different EM counterparts will exhibit different dependence on inclination
angle.  In this subsection, we model an GW+EM catalog composed of two
components.  One component has EM detectable emission only very close to on/off
axis, with $P_{\detected,\EM} = 0$ unless $|x| \geq x_\mathrm{min}$ with
$x_\mathrm{min} = \cos 15^\circ$.  The other component has a (weak) preference
for on/off axis emission, with detectability varying quadratically from a
maximum at $|x| = 1$ to and 1/3 of its maximum value at $x = 0$.  The two
components are mixed equally in the data set, so that the overall EM detection
efficiency is 
\begin{equation}
    P_{\detected,\EM}(x) \propto \frac{1}{2} \left( \frac{H\left( |x| - x_\mathrm{min} \right)}{x_\mathrm{min}} + \frac{3 \left( x^2 + 1/2 \right)}{5} \right),
\end{equation}
with $H$ the Heaviside step function.  We choose $N_l = 4$.  The logarithm of
this function is not expressible as any finite sum of Legendre polynomials, so
our model is incapable of exactly reproducing the shape of this detection
efficiency for any choice of $N_l$.  Nonetheless, we will see that we can still
obtain sub-percent accurate, un-biased estimates of $H_0$, even with only four
additional parameters to describe the EM selection function.

@@

\begin{acknowledgments}
    \todo{We thank people for stuff.}  This work was begun at the KICP workshop
    ``The Quest for Precision Gravitational Wave Cosmology'' in September 2022;
    the authors thank the KICP and workshop organizers for an exceptionally
    stimulating environment.
\end{acknowledgments}
